---
title: "rbbKultur - Mediathek-Downloader"
description: |
  HowTo download "Mediathek" features for archival purposes
preview: example.png
author:
  - first_name: "Olaf"
    last_name: "Schmalfuß"
    orcid_id: 0000-0002-1919-3848
date: 2018-04-05
output:
  distill::distill_article:
    self_contained: false
draft: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

# rbbKultur - Mediathek-Downloader

## Introduction
For archival or educational purposes it might be useful to know how to download content from public radio and TV broadcasters' archives, i.e. "Mediathek".

## 1. select Program
* rbbKultur - Mediathek

> https://www.kulturradio.de/zum_nachhoeren/

  + chose date and program
  
## 2. inspect element
* i.e. launch _Developer Tools_
    + FireFox: CTRL+SHIFT+C
    + Chrome: CTRL+SHIFT+I

## 3. Start player

## 4. back in Developer Tools
* under _NETWORK_ right click on the _File_ (media/ mpeg)
* then _Copy URL_ or _copy as cURL_

## 5. Download via bash script
* adjust script  

```{r, eval=F, echo=T}
rbb_downloader "Program_Name" "Download_URL"

```
  
  
```{r, eval=F, echo=T}
rbb_downloader()
  {
    if [ -z "$1" ]
      then echo "Dateiname fehlt"
    elif [ -z "$2" ]
      then  "Download URL fehlt"
    else
      DWNDIR=/tmp/Downloads/AlteMusik
      AMDOWN=$1
      rbbmediapmdp=$2
      curl $rbbmediapmdp -o $DWNDIR/"$AMDOWN"
      ls -htl $DWNDIR
  fi
  }
  
# usage:
rbb_downloader "Program_Name" "Download_URL"

```

* optional: save in bashrc

> C:\\cygwin64\\home\\schmalfuss\\.bashrc
  
* run
  + e.g.  
  
```{r, eval=F, echo=T}
rbb_downloader "Alte Musik - 2020-07-08 - Heinrich Isaac - Lieder und Motetten.mp3" "https://rbbmediapmdp-a.akamaihd.net/content/74/da/74da3627-5312-4f34-b681-93c48f12202d/0a858af8-b788-430b-9f5a-b5c678701a18_53d97702-265a-4586-a6d8-c8c7ad9bac80.mp3"
```



